Multilocus Genotype And Mycelial Compatability Group Assessment

### 2017-07-26 doc/RMD/mlg-mcg.Rmd
Add analysis of connection

>>>>

The opposite question is, how connected is this huge hairy mess? The community
analysis gave us an idea of where different centers lie, but it doesn't really
do much for us in actually giving us an idea of what the possabilities for 
connection are. One way we can look at this is by using the `ego()` function to
assess the neighborhood of vertices for a given node order, which is to say the
number of edges away from the node you must travel to visit all your neighbors. 
Order 0 would give us the node itself, and order 1 would give us the degree plus 
one. If we set this degree to a large number, we will find all the possible 
connections.

Here I'm getting a simple measure by counting all the vertices, I'm subtracting
two here because I want to remove the genotype and the MCG associated.

```{r node_order}
# getting the sizes for all genotypes.
sizes <- ego_size(g, 200, nodes = which(grepl("Genotype", V(g)$type)), mode = "all") - 2
table(sizes)
```

Here we can see there are 12 genotypes that are only associated with themselves
and their respective MCGs. This corresponds with the results we found above. Up
next are the genotypes that are associated with another partner, which could
represent either two MCGs to one genotype (there are three of these), or two 
genotypes to one MCG. By logical deduction, we can see that there are 5 of these
left. The rest of the entries are not so easy to parse, but it's clear that 
there are 130 genotypes that all have the ability to reach each other through
mutual mycelial compatibility groups.

To focus on strictly the MLGs, we can see a more clear picture. Here, we are
taking the results of `ego()` and counting how many MLGs are in the vertex list.
From there, we can tabulate the results and divide the number of entries by the
category, giving us the number of communities in each category.

```{r community_counting2}
ncommunities <- ego(g, 200, nodes = which(grepl("Genotype", V(g)$type)), mode = "all") %>%
  map_int(. %>% names %>% grepl("MLG", .) %>% sum) %>%
  table() %>%
  {./as.integer(names(.))}
ncommunities
map_dbl(as.integer(names(ncommunities)), choose, 2)
```

From here, we can see that we have 15 MLGs that only interact with themselves,
3 pairs of MLGs, 1 triplet, 1 hendeclet, and 1 community with 130 members, of
which there are 8385 possible combinations.

Of course, the 8385 possible combinations doesn't give us an idea of what the
number of immediately possible combinations exist. We can examine that by 
setting the mode to 2.

```{r community_counting, fig.width = 5, fig.height = 3}
in_reach <- ego(g, 2, nodes = which(grepl("Genotype", V(g)$type)), mode = "all") %>%
  map(function(.x) .x[grepl("MLG", names(.x))])
lengths(in_reach) %>%
  enframe(name = "index", value = "N") %>%
  ggplot(aes(x = N - 1)) +
  geom_histogram(binwidth = 1, center = 0, color = "black", fill = "grey50") +
  theme_bw(base_size = 16, base_family = "Helvetica") +
  theme(aspect.ratio = 1/2) +
  theme(axis.text = element_text(color = "black")) +
  scale_y_continuous(expand = c(0, 0.1)) +
  scale_x_continuous(expand = c(0, 0.1), breaks = c((0:6)*10), limits = c(-1, 60)) +
  theme(panel.grid.major = element_line(colour = "grey20")) +
  theme(panel.grid.minor = element_line(colour = "grey50", linetype = 3)) +
  theme(panel.grid.major.x = element_blank()) +
  theme(panel.grid.minor.x = element_blank()) +
  theme(panel.border = element_blank()) +
  xlab("Number of MLG Neigbors")
```

The maximum here is `r max(lengths(in_reach))`, which represents MLG 25.
